This tiny document was compiled to support my someone's efforts to learn French\nolinebreak\emoji{fr} in school.
It's a bit special compared to official books\footnote{Well, Parallelwörter are helpful to learn...? ``Es gibt viele
Parallelwörter, für die es sinnvoll ist, sie multilingual zu erlernen.'' in MEHRSPRACHIGKEIT IM UNTERRICHT, Adrian Lehmann via
\url{https://phsg.contentdm.oclc.org/digital/api/collection/p15782coll2/id/1151/download}}
\footnote{See also \url{https://de.wikipedia.org/wiki/Liste_deutscher_W\%C3\%B6rter_in_anderen_Sprachen}}
as I mix in English \emoji{uk}, German \emoji{de} and Italian \emoji{it}, hoping that he could re-use my ``Eselsbrücken''
(mnemonics, trucs\footnote{truc - ``Quelque chose dont on ne connait pas le nom, ou dont on se méfie'' from
\url{https://fr.wiktionary.org/wiki/truc} - \emoji{de} Zeug \emoji{uk} stuff} mnémotechnique) to ease learning.
Maybe call it: Dad's superfluous lecture notes or Repetitorium\footnote{https://de.wikipedia.org/wiki/Repetitorium} cheatsheet. YMMV.

{\huge \emoji{warning} \emoji{construction-worker}}

I'm no teacher. Nobody reviewed this document for errors, it's a constant, incomplete work-in-progress, so use at your own risk -- provided as-is, no warranties!

The selection of words (animals, food, ...) has been mostly inspired by
\href{https://twitter.com/unicode}{Unicode} emoji as listed in \url{https://ctan.math.washington.edu/tex-archive/macros/luatex/latex/emoji/emoji-doc.pdf}

That emoji \LaTeX\ package has also been used to typeset all the emoji\footnote{``What's the Plural of Emoji?
There is a correct answer, but no one has agreed on it yet.''
By Robinson Meyer at \url{https://www.theatlantic.com/technology/archive/2016/01/whats-the-plural-of-emoji-emojis/422763/}} used throughout this document.
Many translations in here have been borrowed from \url{https://dict.leo.org/} or lent from
\url{https://translate.google.com} and most conjugations have been stolen from \url{https://pons.com}
-- please don't tell anybody. I have zero intent to monetarise this document, it's public domain;
feel free to recycle arbitrary amounts of it without referring to my raid.
Instead, please redirect your readers to free, quality online resources like stated above.
